A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2020-05-14 manuscript.Rmd
include nutshell figure

In this tutorial, we describe a workflow to ensure long-term and cross-platform reproducibility of data analyses in R [@baseR]. Reproducibility is the ability to draw identical conclusion from the same statistical analysis and the same data. In practice, reproducibility means to us that statistical results as well as their generating computational workflows are reported fully, and transparently, and remain sustainably available, such that a given workflow can be re-run by a different person, later in time, and that the results will be identical to the ones intially reported [@turingway2020; @herouxCompatibleReproducibilityTaxonomy2018; @claerboutElectronicDocumentsGive1992]. The need to ensure reproducibility directly follows from commonly accepted rules of good scientific practice [such as the guidelines of the German Research Foundation, @dfg2019]. Ensuring reproducibility is a prerequisite for replicability (the ability to reach a similar conclusion from the same analysis and new data), and a means to increase trustworthiness of empirical results [@epskamp2019rep]. Transparency and accessibility are  central scientific values and open, reproducible code will increase the efficiency and veracity of knowledge accumulation [@nosek2012scientific].

@@

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components central to a reproducible workflow: version control (git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). "}
knitr::include_graphics("Images/placeholder.png")
```

>>>>

In this tutorial, we describe a workflow to ensure long-term and cross-platform reproducibility of data analyses in R [@baseR]. Reproducibility is the ability to draw identical conclusion from the same statistical analysis and the same data. In practice, reproducibility means to us that statistical results as well as their generating computational workflows are reported fully, and transparently, and remain sustainably available, such that a given workflow can be re-run by a different person, later in time, and that the results will be identical to the ones intially reported [@turingway2020; @herouxCompatibleReproducibilityTaxonomy2018; @claerboutElectronicDocumentsGive1992]. The need to ensure reproducibility directly follows from commonly accepted rules of good scientific practice [such as the guidelines of the German Research Foundation, @dfg2019]. Ensuring reproducibility is a prerequisite for replicability (the ability to reach a similar conclusion from the same analysis and new data), and a means to increase trustworthiness of empirical results [@epskamp2019rep]. Transparency and accessibility are  central scientific values and open, reproducible projects will increase the efficiency and veracity of knowledge accumulation [@nosek2012scientific].

@@

```{r schematic, eval = TRUE, echo = FALSE, fig.cap="Schematic illustration of the interplay of the four components central to a reproducible workflow: version control (git), dependency management (Make), containerization (Docker), and dynamic document generation (R Markdown). "}
knitr::include_graphics("Images/nutshell.svg", auto_pdf = TRUE)
```
